---
title: "p8105_hw1_yc4198.Rmd"
author: "Yining Chen"
date: "2022-09-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,message=FALSE}
library(ggplot2)
library(tidyverse)
```

## Problem 1

The dataset has 344 rows and 8 columns, including 3 factor variables and 5 numeric variables which are species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, year. The below table shows the first 5 rows of the dataset. The mean flipper length is 200.9152 mm.
```{r}
data("penguins", package = "palmerpenguins")
head(penguins,5)
skimr::skim(penguins)
```
```{r,warning=FALSE}
ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm,color=species)) +
  geom_point() +ggtitle("Scatterplot of of Flipper Length vs Bill Length")+labs(y = "Flipper length (mm)", x = "Bill length (mm)")
ggsave("q1_plot.pdf")
```

## Question 2

```{r pressure, echo=FALSE}
set.seed(123)

df = tibble(
  x = rnorm(10, mean= 0,sd = 1),
  vec_char = rep("num", 10) ,
  vec_logical = ifelse(x[1:10]>0,TRUE,FALSE),
  vec_factor = rep(factor(LETTERS[1:3]),4,length.out = 10)
)
```

When taking the mean pf each variable, it works for the random sample x and the logical vector and does not work for the character variable and the factor variable.

```{r}
mean(pull(df,x))
mean(pull(df,vec_char))
mean(pull(df,vec_logical))
mean(pull(df,vec_factor))
```

When I applied the as.numeric function to the logical, character, and factor variables, logical vectors were turned into 0 and 1, factor vectors were turned into 1, 2 and 3, but the character vectors became NAs. This might because logic variables only have two values and the levels for factor variables are also countable. While character variables cannot be categorized into a countable number of values or levels.

```{r,results='hide'}
as.numeric(pull(df,vec_char))
as.numeric(pull(df,vec_logical))
as.numeric(pull(df,vec_factor))
```

